---
title: 'hw03: Linear Regression'
author: "Your name^[affiliation]"
date: '`r format(Sys.time(), "%d %m, %Y")`'
output: pdf_document
---

Questions in this problem set are taken from *Kleiber, C., & Zeileis, A. (2008). Applied econometrics with R. Springer Science & Business Media, pp. 91-92 (questions 2 - 5).*

# Question 2

Estimate a hedonic regression for the HousePrices data taken from Anglin and Gen¸cay (1996), which contain prices of houses sold in the city of Windsor, Canada, during July, August, and September 1987. These data are also used in the textbook by Verbeek (2004).

## a)

Fit a multiple linear regression model to the logarithm of the price,
using all remaining variables as regressors. Experiment with models
containing lot size, number of bathrooms, number of bedrooms, and
stories in logarithms and in levels, respectively. Which model do you
prefer?


```{r}
# Write here your codes

```

<!-- Write your answer here -->







<!-- End of answer  -->

## b)

What is the expected price of a two-story house of 4,700 sq. ft. with
three bedrooms, two bathrooms, a driveway, no recreational room, a
full finished basement, without gas heating or air conditioning, and
two-car garage, that is not located in a preferred area? Report also a
prediction interval.


```{r}
# Write here your codes

```

<!-- Write your answer here -->







<!-- End of answer  -->

## c) 

In order to determine whether the logarithmic transformation of the
dependent variable is really appropriate, a Box-Cox transformation
might be helpful. Use the function ```boxcox()``` from the package **MASS**.
What do you conclude?


```{r}
# Write here your codes

```

<!-- Write your answer here -->







<!-- End of answer  -->

# Question 3

Consider the ```PSID1982``` data from Cornwell and Rupert (1988) and discussed
further in Baltagi (2002).

## a) 

Regress the logarithm of the wage on all available regressors plus experience
squared.


```{r}
# Write here your codes

```


## b) 

Does gender interact with education and/or experience?

<!-- Write your answer here -->







<!-- End of answer  -->


# Question 4

Section 3.5 considered two competing models for US consumption utilizing
an encompassing test. Different approaches to comparing nonnested models are the J test suggested by Davidson and MacKinnon (1981) and the Cox test. Both are available in the package **lmtest** in the functions ```jtest()``` and ```coxtest()```. For the methodological background, we refer to Greene (2003, Chapter 8) and Davidson and MacKinnon (2004).

## a) 

Test ```cons_lm1``` vs. ```cons_lm2``` using the J test.


```{r}
# Write here your codes

```


## b)

Test ```cons_lm1``` vs. ```cons_lm2``` using the Cox test.


```{r}
# Write here your codes

```

Do all tests lead to similar conclusions?



<!-- Write your answer here -->







<!-- End of answer  -->


# Question 5

Use the ```PSID1982``` data and consider the following two nonnested models
(compare with Baltagi 2002, p. 230):

$$
\begin{aligned}
M_{1}: log(wage) = 
\beta_{0} + \beta_{1}education + \beta_{2}experience + \\ \beta_{3}experience^{2}  
+ \beta{4}weeks + \beta_{5}married + \\
\beta_{6}gender  + \beta_{7}ethnicity + \beta_{8}union + \epsilon 
\end{aligned}
$$
$$
\begin{aligned}
M_{2}: log(wage) = \beta_{0} + \beta_{1}education + \beta_{2}experience \\
+ \beta_{3}experience^{2} + \beta{4}weeks + \beta_{5}occupation \\
+ \beta_{6}south + \beta_{7}smsa + \beta_{8}industry + \nu
\end{aligned}
$$



## a) 

Compute the J tests for $M_{1}$ vs. $M_{2}$ and $M_{2}$ vs. $M_{1}$, respectively.

```{r}
# Write here your codes

```

## b)

Both $M_{1}$  and $M_{2}$ can be artificially nested within a larger model. Use an F test for $M_{1}$  versus this augmented model. Repeat for $M_{2}$ versus the augmented model. What do you conclude?


```{r}
# Write here your codes

```

<!-- Write your answer here -->







<!-- End of answer  -->